Make any stupid plot you want

### 2021-01-26 draft/sections/math.tex
artist picture

\subsubsection{Display $D$}
\label{sec:graphic_fiber}
The fiber $D$ is specified in terms of the target display space, for example a 2D screen or 3D printer. In this work, we assume a simple 2D opaque image $D=\mathbb{R}^5$ with a record $d \in D$ of the form
\begin{equation}
    d = (x, y, r, g, b)
\end{equation}
such that a graphic only has 2D position and color. To support overplotting and transparency, the fiber would be $D=R^{7}$ such that $d=(x, y, z, r, g, b, a)$. The location coordinates $x$ and $y$ are defined in terms of the display, while the $(r,g,b)$ values are filled in via a lookup on $S$.

@@

In figure~\ref{fig:graphic_retraction_map} each disk $S_k$ indexes how the records in $D$ are held together to generate a single glyph that is the visual representation of a single point in $F_k$. For the line, the region $\beta$ over a point $\alpha_i$ specifies the thickness of the line in $D$ for the corresponding section on the interval $K$. The heatmap has the same continuity in data space and graphic space such that no extra dimensions are needed.

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/graphic_render.png}
    \caption{To render a graphic, a region $b$ is selected in the display space. This region is in coordinates $D$ so the inverse mapping $\rho^{-1}(b)$ maps to an equivalent region $S_b \subset S$. We then take the sections $\rho(S_b)$ which are the collection of records $d$ that combine together to make the piece of the graphic in $b$.}
    \label{fig:graphic_rho_lookup}
\end{figure}
As shown in figure~\ref{fig:graphic_rho_lookup}, the output space queries into the graphic bundle to render the image. We select a region $b$ in the output space, inverse map the region into $S_b \subset S$, then take the section $\rho$ over the region $S_b$ which yields a set of corresponding records $d$. These records specify the $(r, g, b)$ values corresponding to the coordinates in $b$. These records are then combined to render the piece of the graphic in $b$.

\subsection{Artist}
\label{sec:artist}

%% E' not E
In this section we will define the artist as a mapping from a sheaf $\mathcal{O}(E)$  to $\mathcal{O}(H)$. 
\begin{equation}
    A: \mathcal{O}(E) \rightarrow \mathcal{O}(H)
\end{equation}

The artist decomposes to mapping data to visual $\nu:E\rightarrow V$, then  compositing $V$ pulled back along $\xi$ to $\xi^*V$ to a visual mark in prerender space $Q:\xi^*V\rightarrow H$.

@@

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $\{f_{0}, \ldots, f_{n}\} \times (\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
    \label{tab:mpl_visual_variable_fiber}
\end{table}

>>>>

\subsubsection{Display $D$}
\label{sec:graphic_fiber}
The fiber $D$ is specified in terms of the target display space, for example a 2D screen or 3D printer. In this work, we assume a simple 2D opaque image $D=\mathbb{R}^5$ with an element $d \in D$ of the form
\begin{equation}
    d = (x, y, r, g, b)
\end{equation}
such that a graphic only has 2D position and color. To support overplotting and transparency, the fiber would be $D=R^{7}$ such that $d=(x, y, z, r, g, b, a)$. The location coordinates $x$ and $y$ are defined in terms of the display, while the $(r,g,b)$ values are filled in via a lookup on $S$.

@@

In figure~\ref{fig:graphic_retraction_map} each disk $S_k$ indexes how elements in $D$ are held together to generate a single glyph that is the visual representation of a single point in $F_k$. For the line, the region $\beta$ over a point $\alpha_i$ specifies the thickness of the line in $D$ for the corresponding section on the interval $K$. The heatmap has the same continuity in data space and graphic space such that no extra dimensions are needed.

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/graphic_render.png}
    \caption{To render a graphic, a region $b$ is selected in the display space. This region is in coordinates $D$ so the inverse mapping $\rho^{-1}(b)$ maps to an equivalent region $S_b \subset S$. We then take the sections $\rho(S_b)$ which are the elements $\{d_0, \ldots, d_n\}$ that make the piece of the graphic in $b$.}
    \label{fig:graphic_rho_lookup}
\end{figure}
As shown in figure~\ref{fig:graphic_rho_lookup}, the output space queries into the graphic bundle to render the image. We select a region $b$ in the output space, inverse map the region into $S_b \subset S$, then take the section $\rho$ over the region $S_b$. The section yields the set of elements $\{d_0, \ldots, d_n\}$ that specify the $(r, g, b)$ values corresponding to the coordinates in $b$.

\subsection{Artist}
\label{sec:artist}
The artist is the composite function that converts data into graphics; its name is taken from the analogous part of the existing Matplotlib architecture. The binding of $\xi:S \rightarrow K$ keeps track of which data goes to which part of the graphic such that the artist can be trivially parallelized or formulated as a delayed computer graph or otherwise not need to immediately work on all the data.

The artist is a mapping from $E$ padded with data from $\mathcal{J}(E)$
\begin{equation}
    A: E^\prime \rightarrow \Gamma(H)
\end{equation}
\note{this is soup}
to a graphic in $\Gamma(H)$. The artist decomposes to mapping data to visual $\nu:E\rightarrow V$, then  compositing $V$ pulled back along $\xi$ to $\xi^*V$ to a visual mark in prerender space $Q:\xi^*V\rightarrow H$.

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/artist_stages.png}
    \caption{The artist $A$ converts data into the visual variables in $V$ and then composes those visual variables into a graphic in $H$}
    \label{fig:artist_stages}
\end{figure}
\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $\{f_{0}, \ldots, f_{n}\} \times (\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
    \label{tab:mpl_visual_variable_fiber}
\end{table}
